Endogenous Macrodynamics in Algorithmic Recourse

### 2022-08-09 dev/paper/sections/limitations.qmd
2/3 real world data done

## Limitations and Future Work {#sec-limit}

@@

>>>>

# Limitations and Future Work {#sec-limit}

While we believe that this work constitutes a valuable starting point for addressing existing issues in algorithmic recourse from a fresh perspective, we are aware of several of its limitations. In the following we highlight some of these limitations and point to avenues for future research.

## Experimental Setup

@@

## Data

Largely in line with the existing literature on algorithmic recourse, we have limited our analysis of real-world data to three commonly used benchmark datasets that involve binary prediction tasks. Future work may benefit from including novel datasets or extending the analysis to multi-class or regression problems, the latter arguably representing the most common objective in Finance and Economics. 
It is also worth mentioning that the use of real-world datasets considered in this work is constrained by the fact that at the time of writing `CounterfactualExplanations.jl` only supports continuous features, at least of some of the counterfactual generators considered here. The fact that we therefore had to discard discrete features led to relatively poor initial performance of our classifiers in some cases. While this is indeed a limitation we intend to address in future and derivative work, our findings with respect to endogenous macrodynamics do not hinge on strong classifier performance.

## Classifiers

For reasons stated earlier we have limited our analysis to differentiable linear and non-linear classifiers, in particular logistic regression and deep neural networks. While these sorts of classifiers have also typically been analyzed in the existing literature on counterfactual explanations and algorithmic recourse, they represent only a subset of popular machine learning models employed in practice - both black-box and glass-box. Despite the success and popularity of deep learning in the context of high-dimensional data such as image, audio and video, empirical evidence suggests that other models such as boosted decision trees may have an edge when it comes to lower-dimensional tabular datasets, such as the ones considered here [@borisov2021deep, @grinsztajn2022tree].
